Improvement of crash forces in structures using optimization tools.

### 2016-07-27 paper.tex
Avances

It must be pointed out that the use of several material with different behaviour formulations including crack formation implies the use of the XFEM. Although it will have some implications in the present section ---and more specifically on \cref{sec:damage}---, the XFEM will be explained afterwards in \cref{sec:xfem} in order to keep some coherence in the explanation.

\subsubsection{Adhesive}
Loctite Hysol 9514 \cite{manufCatalog} was the chosen adhesive for the bonding, for its shown interest by many other authors for structural bonding \cite{Sadowski2010, Scattina2011, SernaMoreno2015}, making it an \textit{a priori} good candidate for the studied application. It is a monocomponent epoxy adhesive which requires heat curing processes in the union cast.

@@

\subsubsection{Adherends}

>>>>

Loctite Hysol 9514 \cite{manufCatalog} was the chosen adhesive for the bonding, for its shown interest by many other authors for structural bonding \cite{Sadowski2010, Scattina2011, SernaMoreno2015}, making it an \textit{a priori} good candidate for the studied application. It is a monocomponent epoxy adhesive which requires heat curing processes in the union cast.

@@
